Community Embeddings for Facebook Friend Suggestions\\ \thanks{The reported study was partially supported by RFBR grant \textnumero 20-07-00958. The paper was prepared within the framework of the HSE University Project Group Competition 2020-2022.}

### 2020-10-14 paper-ffs.tex
Social circles: Facebook -> Social Circles: Facebook
feedback Opa

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/fb/graph_d4.png}
    \caption{\textit{Social circles: Facebook} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
    \label{fig:fb_graph}
\end{figure}

@@

The recommender system based on community embeddings with the Bayesian Gaussian mixture model and variational inference is quantitatively evaluated. Friend suggestions are generated for the \textit{Social circles: Facebook} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.

The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \textit{Social circles: Facebook} graph. Both Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} are evaluated. The top-$N$ recommendations are evaluated by the hit-rate metric.

@@

The \textit{Social circles: Facebook} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \textit{Learning to Discover Social Circles in Ego Networks} \cite{social_circles_in_ego_networks}.

@@

The \textit{Social circles: Facebook} graph is split into training and testing parts. For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
Users with only one connection are removed from the dataset since no network information is added by them.

$1169$ of the 4039 users of the \textit{Social circles: Facebook} graph have at least $50$ connections and are used for testing friend suggestions. The threshold of $50$ friends for considering users for testing is set to make sure enough data is available to make sensable suggestions for testing users.

@@

Community embeddings for the \textit{Social circles: Facebook} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.

\begin{table}
    \centering
    \caption{Hyperparameters used for the \textit{Social circles: Facebook} dataset.}
    \label{tab:params_fb}
    \begin{tabular}{ l | c | r }
        parameter                    & notation & value       \\
        \hline
        \hline
        number\_walks                & $\gamma$ & $10$        \\
        \hline
        walk\_length                 & $\ell$   & $80$        \\
        \hline
        representation\_size         & $D$      & $2, 4, 128$ \\
        \hline
        num\_workers                 & \empty   & $10$        \\
        \hline
        num\_iter                    & \empty   & $3$         \\
        \hline
        com\_n\_init                 & \empty   & $10$        \\
        \hline
        reg\_covar                   & \empty   & $0.00001$   \\
        \hline
        batch\_size                  & \empty   & $50$        \\
        \hline
        window\_size                 & $\zeta$  & $10$        \\
        \hline
        negative                     & $m$      & $5$         \\
        \hline
        lr                           & \empty   & $0.025$     \\
        \hline
        alpha                        & $\alpha$ & $0.1$       \\
        \hline
        beta                         & $\beta$  & $0.1$       \\
        \hline
        down\_sampling               & \empty   & $0.0$       \\
        \hline
        communities                  & $K$      & $10$        \\
        \hline
        weight\_concentration\_prior & $\Gamma$ & $10^{-5}$   \\
    \end{tabular}
\end{table}

As is shown in Table \ref{tab:params_fb}, the embedding's representation size $D$ is varied along three values. A representation size $D \in [2,4,128]$ is chosen to determine the effect of the embedding's dimensionality on friend suggestions. It is hypothesized, that two dimensions are not sufficient to capture the structure of the \textit{Social circles: Facebook} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.

@@

Fig. \ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$. The limiting two-dimensional space does not allow ComE to represent the \textit{Social circles: Facebook} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model. Only three components are used after the last of three iterations.

@@

    \caption{Hit-rates of \textit{Social circles: Facebook} graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$. Hit-rate lines for Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} overlap for $D=2$ and $D=4$.}
    \label{fig:fb_hit_rates}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \caption{Hit-rates of \textit{Social circles: Facebook} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [5, 10, 20]$, and $D \in [2, 4, 128]$.}
    \label{tab:fb_hit_rates}
    \begin{tabular}{ l | l | c | c | c }
        \hline
        \empty                                              & \empty  & top-$5$         & top-$10$        & top-$20$        \\
        \hline
        \hline
        \multirow{3}{*}{Algorithm \ref{alg:friend_sug}}     & $D=2$   & 8.5\%           & 14.2\%          & 21.9\%          \\
                                                            & $D=4$   & 18.1\%          & 26.5\%          & 38.4\%          \\
                                                            & $D=128$ & \textbf{31.3\%} & \textbf{43.6\%} & \textbf{58.8\%} \\
        \hline
        \multirow{3}{*}{Algorithm \ref{alg:friend_sug_com}} & $D=2$   & 8.4\%           & 14.1\%          & 21.8\%          \\
                                                            & $D=4$   & 18.0\%          & 26.4\%          & 38.2\%          \\
                                                            & $D=128$ & \textbf{24.1\%} & \textbf{32.9\%} & \textbf{41.8\%} \\
        \hline
    \end{tabular}
\end{figure}

>>>>

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/fb/graph_d4.png}
    \caption{\textit{Social Circles: Facebook} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
    \label{fig:fb_graph}
\end{figure}

@@

The recommender system based on community embeddings with the Bayesian Gaussian mixture model and variational inference is quantitatively evaluated. Friend suggestions are generated for the \textit{Social Circles: Facebook} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.

The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \textit{Social Circles: Facebook} graph. Both Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} are evaluated. The top-$N$ recommendations are evaluated by the hit-rate metric.

@@

The \textit{Social Circles: Facebook} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \textit{Learning to Discover Social Circles in Ego Networks} \cite{social_circles_in_ego_networks}.

@@

The \textit{Social Circles: Facebook} graph is split into training and testing parts. For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
Users with only one connection are removed from the dataset since no network information is added by them.

$1169$ of the 4039 users of the \textit{Social Circles: Facebook} graph have at least $50$ connections and are used for testing friend suggestions. The threshold of $50$ friends for considering users for testing is set to make sure enough data is available to make sensable suggestions for testing users.

@@

Community embeddings for the \textit{Social Circles: Facebook} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.

\begin{table}
    \centering
    \caption{Hyperparameters used for the \textit{Social Circles: Facebook} dataset.}
    \label{tab:params_fb}
    \begin{tabular}{ l | c | r }
        parameter                    & notation & value       \\
        \hline
        \hline
        number\_walks                & $\gamma$ & $10$        \\
        \hline
        walk\_length                 & $\ell$   & $80$        \\
        \hline
        representation\_size         & $D$      & $2, 4, 128$ \\
        \hline
        num\_workers                 & \empty   & $10$        \\
        \hline
        num\_iter                    & \empty   & $3$         \\
        \hline
        com\_n\_init                 & \empty   & $10$        \\
        \hline
        reg\_covar                   & \empty   & $0.00001$   \\
        \hline
        batch\_size                  & \empty   & $50$        \\
        \hline
        window\_size                 & $\zeta$  & $10$        \\
        \hline
        negative                     & $m$      & $5$         \\
        \hline
        lr                           & \empty   & $0.025$     \\
        \hline
        alpha                        & $\alpha$ & $0.1$       \\
        \hline
        beta                         & $\beta$  & $0.1$       \\
        \hline
        down\_sampling               & \empty   & $0.0$       \\
        \hline
        communities                  & $K$      & $10$        \\
        \hline
        weight\_concentration\_prior & $\Gamma$ & $10^{-5}$   \\
    \end{tabular}
\end{table}

As is shown in Table \ref{tab:params_fb}, the embedding's representation size $D$ is varied along three values. A representation size $D \in [2,4,128]$ is chosen to determine the effect of the embedding's dimensionality on friend suggestions. It is hypothesized, that two dimensions are not sufficient to capture the structure of the \textit{Social Circles: Facebook} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.

@@

Fig. \ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$. The limiting two-dimensional space does not allow ComE to represent the \textit{Social Circles: Facebook} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model. Only three components are used after the last of three iterations.

@@

    \caption{Hit-rates of \textit{Social Circles: Facebook} graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$. Hit-rate lines for Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} overlap for $D=2$ and $D=4$.}
    \label{fig:fb_hit_rates}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \caption{Hit-rates of \textit{Social Circles: Facebook} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [5, 10, 20]$, and $D \in [2, 4, 128]$.}
    \label{tab:fb_hit_rates}
    \begin{tabular}{ l | l | c | c | c }
        \hline
        \empty                                              & \empty  & top-$5$         & top-$10$        & top-$20$        \\
        \hline
        \hline
        \multirow{3}{*}{Algorithm \ref{alg:friend_sug}}     & $D=2$   & 8.5\%           & 14.2\%          & 21.9\%          \\
                                                            & $D=4$   & 18.1\%          & 26.5\%          & 38.4\%          \\
                                                            & $D=128$ & \textbf{31.3\%} & \textbf{43.6\%} & \textbf{58.8\%} \\
        \hline
        \multirow{3}{*}{Algorithm \ref{alg:friend_sug_com}} & $D=2$   & 8.4\%           & 14.1\%          & 21.8\%          \\
                                                            & $D=4$   & 18.0\%          & 26.4\%          & 38.2\%          \\
                                                            & $D=128$ & \textbf{24.1\%} & \textbf{32.9\%} & \textbf{41.8\%} \\
        \hline
    \end{tabular}
\end{figure}
